D3064R0: How to Avoid OOTA Without Really Trying

### 2024-03-03 ootavacuous.tex
"But What About Tooling": Reword
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

One entirely reasonable reaction is that, given the issues raised in
Sections~\ref{sec:Properties of Semantic Dependencies}
and~\ref{sec:The Fundamental Property of Semantic Dependencies},
load/store reordering is the least of the problems faced by tooling.
Nevertheless, this appendix expands on
Section~\ref{sec:Semantic Dependencies and Tooling}
by looking into the possibility of:
\begin{itemize}
\item	Tooling focusing on only part of the language,
\item	Changing the language to eliminate some aspects that are
	troublesome for tooling (and potentially accepting performance
	and energy-efficiency shortfalls), and
\item	Changing the language to better delineate those portions that
	tooling can easily accommodate.
\end{itemize}

But first, the next section looks at why some weakly ordered
implementations appear to forbid reordering of prior relaxed loads with
later relaxed stores,\footnote{
	Or, in memory-order-speak, forbid all load-buffering litmus tests.}
despite the architecture permitting such reordering.

@@

Tooling does not require relaxed accesses become fully acquire and/or
release, but rather only that implemetnations be forbidden from reordering
prior relaxed loads with subsequent relaxed stores, as has been suggested
many times over the
years~\cite{Boehm:2014:OGA:2618128.2618134,HansBoehm2019OOTArevisitedAgain,Lahav:2017:RSC:3062341.3062352}.

>>>>

One entirely reasonable reaction is that, given the issues raised in
Section~\ref{sec:Properties of Semantic Dependencies},
Section~\ref{sec:C++ Compilers},
and
Section~\ref{sec:Outstanding Issues},
load/store reordering is the least of the problems faced by tooling.
Nevertheless, this appendix expands on
Section~\ref{sec:Semantic Dependencies and Tooling}
by looking into the possibility of:
\begin{itemize}
\item	Tooling focusing on only part of the language,
\item	Changing the language to eliminate some aspects that are
	troublesome for tooling (and potentially accepting performance
	and energy-efficiency shortfalls), and
\item	Changing the language to better delineate those portions that
	tooling can easily accommodate.
\end{itemize}

But first, the next section looks at why some weakly ordered
computer hardware appears to forbid reordering of prior relaxed loads with
later relaxed stores,\footnote{
	Or, in memory-order-speak, forbid all load-buffering litmus tests.}
despite the architecture permitting such reordering.

@@

Tooling does not require relaxed accesses become fully acquire and/or
release, but rather only that implementations be forbidden from reordering
prior relaxed loads with subsequent relaxed stores, as has been suggested
many times over the
years~\cite{Boehm:2014:OGA:2618128.2618134,HansBoehm2019OOTArevisitedAgain,Lahav:2017:RSC:3062341.3062352}.
